---
title: "During vs. after booms/busts"
output: github_document
---

Comparing what happens during vs. after a boom/bust (stress, burnout)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(anomaly)
library(tidyverse)
library(skimr)
library(nlme)
library(ggplot2)
library(effects)
library(psych)
```

Load anomaly data 
```{r, message = F, warning = F}
load(file="d.an.Rdata")

# Remove teams with no anomalies
d.an <- d.an %>%
  filter(!is.na(anomalies.count))
```

Stress during/after a boom
Variable "after.boom.phase" is a dummy that is coded with 0= during a boom, and 1 = after a boom (first 4 measurements after a boom)
```{r}
# Likelihood check
model_1r <- lme(fixed = s.em1 ~ s.pas + after.boom.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, method = "ML")

model_1br <- lme(fixed = s.em1 ~ s.pas + s.pas*after.boom.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, method = "ML")

anova(model_1r, model_1br)

## Second model is best (with interaction)

# Interaction with boom 
model_1b <- lme(fixed = s.em1 ~ s.pas + s.pas*after.boom.phase,
                   random = ~1 | team, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_1b)
```

Plots for stress during/after boom:
```{r}
eff <- effect("s.pas:after.boom.phase", xlevels = list(after.boom.phase = c(0, 1)), model_1b)

effdata <- as.data.frame(eff)

effdata$after.boom.phase <- as.factor(effdata$after.boom.phase)

plot <- ggplot(effdata, aes(x = s.pas, y = fit, color = after.boom.phase, group = after.boom.phase)) +
  geom_point() +
  geom_line(size = 1.2) + 
  labs(title = "Stress", x= "Individual passion", y="Stress", color="During or after boom?", fill="During or after boom?") + theme_classic() + theme(text=element_text(size=12)) + 
  scale_fill_discrete(labels = c("During boom", "After boom")) +   scale_color_discrete(labels = c("During boom", "After boom"))

plot
```

Burnout
```{r}
# Likelihood check
model_2r <- lme(fixed = s.b2 ~ s.pas + after.boom.phase ,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, method = "ML")

model_2br <- lme(fixed = s.b2 ~ s.pas + after.boom.phase + s.pas*after.boom.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, method = "ML")

anova(model_2r, model_2br)

## Second model with interaction is best

## Predicting future burnout from previous passion + interaction with boom 
model_2b <- lme(fixed = s.b2 ~ s.pas + after.boom.phase + s.pas*after.boom.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit)

summary(model_2b)
```

> Higher individual passion predicts lower burnout next measurement (main effect). Burnout is lower following a boom (main effect). Relationship between passion and next-measurement burnout is less strong if this occurs following a boom (interaction). 

Plots:
```{r}
eff <- effect("s.pas:after.boom.phase", xlevels = list(after.boom.phase = c(0, 1)), model_2b)

effdata <- as.data.frame(eff)

effdata$after.boom.phase <- as.factor(effdata$after.boom.phase)

plot <- ggplot(effdata, aes(x = s.pas, y = fit, color = after.boom.phase, group = after.boom.phase)) +
  geom_point() +
  geom_line(size = 1.2) + 
  labs(title = "Burnout", x= "Individual passion", y="Burnout", color="During or after boom?", fill="During or after boom?") + theme_classic() + theme(text=element_text(size=12)) + 
  scale_fill_discrete(labels = c("During boom", "After boom")) +   scale_color_discrete(labels = c("During boom", "After boom"))

plot
```

Stress during/after bust 
```{r}
# Likelihood check
model_3r <- lme(fixed = s.em1 ~ s.pas + after.bust.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, method = "ML")

model_3br <- lme(fixed = s.em1 ~ s.pas + after.bust.phase + s.pas*after.bust.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, method = "ML")

anova(model_3r, model_3br)

## Second model is best

## Predicting stress during/after bust 
model_3b <- lme(fixed = s.em1 ~ s.pas + after.bust.phase + s.pas*after.bust.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_3b)
```

Plots:
```{r}
eff <- effect("s.pas:after.bust.phase", xlevels = list(after.bust.phase = c(0, 1)), model_3b)

effdata <- as.data.frame(eff)

effdata$after.bust.phase <- as.factor(effdata$after.bust.phase)

plot <- ggplot(effdata, aes(x = s.pas, y = fit, color = after.bust.phase, group = after.bust.phase)) +
  geom_point() +
  geom_line(size = 1.2) + 
  labs(title = "Stress", x= "Individual passion", y="Stress", color="During or after bust?", fill="During or after bust?") + theme_classic() + theme(text=element_text(size=12)) + 
  scale_fill_discrete(labels = c("During bust", "After bust")) +   scale_color_discrete(labels = c("During bust", "After bust"))

plot
```

Burnout during/after bust 
```{r}
# Likelihood check
model_4r <- lme(fixed = s.b2 ~ s.pas + after.bust.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, method = "ML")

model_4br <- lme(fixed = s.b2 ~ s.pas + after.bust.phase + s.pas*after.bust.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, method = "ML")

anova(model_4r, model_4br)

## Second model is best

## Burnout during/after bust 
model_4b <- lme(fixed = s.b2 ~ s.pas + after.bust.phase + s.pas*after.bust.phase,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_4b)
```

Plots:
```{r}
eff <- effect("s.pas:after.bust.phase", xlevels = list(after.bust.phase = c(0, 1)), model_4b)

effdata <- as.data.frame(eff)

effdata$after.bust.phase <- as.factor(effdata$after.bust.phase)

plot <- ggplot(effdata, aes(x = s.pas, y = fit, color = after.bust.phase, group = after.bust.phase)) +
  geom_point() +
  geom_line(size = 1.2) + 
  labs(title = "Burnout", x= "Individual passion", y="Burnout", color="During or after bust?", fill="During or after bust?") + theme_classic() + theme(text=element_text(size=12)) + 
  scale_fill_discrete(labels = c("During bust", "After bust")) +   scale_color_discrete(labels = c("During bust", "After bust"))

plot
```