---
title: "Length of booms/busts"
output: github_document
---

Comparing short and long booms/busts
Booms/busts can be between 3 and 9 measurements long. I recoded length of 6 and higher as long (so 6,7,8 or 9) with 2, and below 6 as short (so 3, 4, or 5) with 1. 

I created dummy variables to indicate whether the measurement occured after a long or short boom/bust. This is the column after.boom.length.d or after.bust.length.d (2 = after long one, 1 is after short one, 0 = during boom/bust)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(anomaly)
library(tidyverse)
library(skimr)
library(nlme)
library(ggplot2)
library(effects)
library(psych)
```

Load anomaly data 
```{r, message = F, warning = F}
load(file="d.an.Rdata")

# Remove teams with no anomalies
d.an <- d.an %>%
  filter(!is.na(anomalies.count))
```

Stress during/after a boom
The column after.boom.length.d indicates the difference between a long and short boom (2 = after long boom, 1 is after short boom, 0 = during boom/bust) --> so this compares stress after a long/short boom vs. during
```{r}
d.an$after.boom.length.d <- as.factor(d.an$after.boom.length.d)

model_1 <- lme(fixed = s.em1 ~ after.boom.length.d,
                   random = ~1 | team, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_1)
```
> Stress is higher after a long boom than after a short boom 

Burnout
```{r}
model_2 <- lme(fixed = s.b2 ~ after.boom.length.d,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit)

summary(model_2)
```

> Burnout is higher after a long boom than after a short boom

Stress during/after bust 
```{r}
d.an$after.bust.length.d <- as.factor(d.an$after.bust.length.d)

model_3 <- lme(fixed = s.em1 ~ after.bust.length.d,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_3)
```
> Stress is slightly lower after a long bust than after a short bust. 

Burnout during/after bust 
```{r}
model_4 <- lme(fixed = s.b2 ~ after.bust.length.d,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_4)
```
> Burnout is slightly lower after a short (!) bust than after a long bust.
