---
title: "Anomalies in passion team average"
output: github_document
---

> Detecting anomalies in average team passion (momentary mean of the team)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(anomaly)
library(tidyverse)
```

```{r, message = F, warning = F}
load(file="d.Rdata")
```

Team average passion
```{r}
d <- d %>%
  group_by(pid) %>%
  mutate(m = 1:n()) %>%
  ungroup()

# There are 10 measurements with missings on passion, I delete these 
d <- d %>%
  filter(!is.na(s.pas))

# Team passion average and SD per measurement
d <- d %>%
  group_by(m, team) %>%
  mutate(sd.pas = sd(s.pas, na.rm=TRUE),
         mean.pas = mean(s.pas, na.rm=TRUE)) %>%
  ungroup()
```

Select one team to try out
```{r}
d_1010 <- d %>%
  filter(team == 1010) 

# Select data at team-level 
d_1010.2 <-d_1010 %>%
  group_by(m) %>%
  slice(1) %>%
  ungroup()
```

CAPA: Anomalies in momentary team average. For the collective anomalies, I select a period of 3 measurement points (1 day) as the minimum and 15 points (5 days). 
```{r}
res.1010 <- capa.uv(d_1010.2$mean.pas, min_seg_len = 6, max_seg_len = 15, type = "robustmean")

# Select collective anomalies
col.1010 <- collective_anomalies(res.1010)
                    
head(col.1010)
plot(res.1010)
```

Now for all teams. Create dataframe to store start and end of anomalies + variable that indicates whether measurement point falls in the anomaly period (section).  
```{r}
d_t <-d %>%
  group_by(team, m) %>%
  slice(1) %>%
  ungroup()

df <- d_t[order(d_t$m),] 
df <- df %>%
  select(team, m, mean.pas)

df['start'] <- NA
df['end'] <- NA 
df['section'] <- NA
```

The capa.uv function resulted in errors for some teams:
```{r}
x <- df
for (i in unique(x$team)) {
  tryCatch({
    res.capa <-
      capa.uv(
        x$mean.pas[x$team == i],
        min_seg_len = 6,
        max_seg_len = 15,
        type = "robustmean"
      )
    res <- collective_anomalies(res.capa)
    cat("For team", i, "'Res' has", nrow(res), "rows.\n")
  }, error = function(e) {
    message("ERROR: Team ", i, ": ", conditionMessage(e))
  })
}
```

Errors for the following teams: 1024, 1025, 1027, 1028, 1030, 1031, 1032, 1033, 1034, 1036, 1051, 1055, 1056, 1058, 1072, 1073, 1077, 1084, 1086, 1090, 1092, 1097, 1098, 1099, 1117, 1151, 2201.

Examine if this is due to low variance (robust MAD):
```{r}
# 1024 as example
x <- df
i <- 1024 # team
x$mean.pas[x$team == i] # look at raw data: lots of scores are the same
median(x$mean.pas[x$team == i]) # check robust central tendency
mad(x$mean.pas[x$team == i]) # check robust variance: MAD is 0 
rm(x, i, res.capa, res)

# Low variance in mean scores happens in all teams in which I get error messages:
df %>%
  group_by(team) %>%
  dplyr::summarise(mad = mad(mean.pas)) %>%
  arrange(mad)

# I remove those teams
df <- df %>%
  group_by(team) %>%
  dplyr::mutate(mad = mad(mean.pas))

df <- df %>%
  filter(mad > 0)

df <- df %>%
  select(-mad)

n_distinct(df$team)
# This leaves 128 teams
```


```{r, warning=F}
get.an.Ignore <- function(x) {
  # FOR TESTING:
  # x = df
  # i = 1024
  
  for (i in unique(x$team)) {
    # reset for error handling
    res.capa <- NA
    
    tryCatch({
      res.capa <-
        capa.uv(
          x$mean.pas[x$team == i],
          min_seg_len = 6,
          max_seg_len = 15,
          type = "robustmean"
        )
      res <- collective_anomalies(res.capa)
      cat("Team", i, "has", nrow(res), "anomalous segments.\n")
    }, error = function(e) {
      message("ERROR: Team ", i, ": ", conditionMessage(e))
    })
    
    if (is.na(res.capa)) { # If error detected
      x[x$team == i,] <-
        x %>%
        filter(team == i) %>%
        mutate(start = NaN, # set to NaN to distinguish it from unprocessed or working values
               end = NaN) # set to NaN to distinguish it from unprocessed or working values
      
    } else if (nrow(res) > 0) { # If anomaly detected
      x[x$team == i,] <-
        x %>%
        filter(team == i) %>%
        mutate(start = ifelse(m %in% res$start, 1, 0),
               end = ifelse(m %in% res$end, 1, 0))
      
    } else { # If no anomaly detected
      x[x$team == i,] <-
        x %>%
        filter(team == i) %>%
        mutate(start = -99, # set to -99 to distinguish it from unprocessed NAs could be set to 0 or NA instead
               end = -99) # set to -99 to distinguish it from unprocessed NAs could be set to 0 or NA instead
    }
  }
  return(x)
}
AnIgnoreError <- get.an.Ignore(df)

```

I added three variables to the dataframe to indicate whether a measurement point was a start of an anomaly (start), end (end), and it is in the anomaly period (section):

```{r, warning = F}
get.an.Section.Ignore <- function(x) {
  # FOR TESTING:
  # x = df
  # i = 1010
  
  for (i in unique(x$team)) {
    # reset for error handling
    res.capa <- NA
    
    tryCatch({
      res.capa <-
        capa.uv(
          x$mean.pas[x$team == i],
          min_seg_len = 6,
          max_seg_len = 15,
          type = "robustmean"
        )
      res <- collective_anomalies(res.capa)
      cat("Team", i, "has", nrow(res), "anomalous segments.\n")
    }, error = function(e) {
      message("ERROR: Team ", i, ": ", conditionMessage(e))
    })
    
    if (is.na(res.capa)) { # If error detected
      x[x$team == i,] <-
        x %>%
        filter(team == i) %>%
        mutate(start = NaN, # set to NaN to distinguish it from unprocessed or working values
               end = NaN, # set to NaN to distinguish it from unprocessed or working values
               section = NaN) # set to NaN to distinguish it from unprocessed or working values
      
    } else if (nrow(res) > 0) { # If anomaly detected
      
      anomalySection <- mapply(seq, res$start, res$end, SIMPLIFY = FALSE) %>% unlist
        
      x[x$team == i,] <-
        x %>%
        filter(team == i) %>%
        mutate(start = ifelse(m %in% res$start, 1, 0),
               end = ifelse(m %in% res$end, 1, 0),
               section = ifelse(m %in% anomalySection, 1, 0))
      
    } else { # If no anomaly detected
      x[x$team == i,] <-
        x %>%
        filter(team == i) %>%
        mutate(start = -99, # set to -99 to distinguish it from unprocessed NAs could be set to 0 or NA instead
               end = -99, # set to -99 to distinguish it from unprocessed NAs could be set to 0 or NA instead
               section = -99) # set to -99 to distinguish it from unprocessed NAs could be set to 0 or NA instead
    }
  }
  return(x)
}

anomalies <- get.an.Section.Ignore(df) %>% arrange(team)
```

There are several teams with no anomalies (indicated with -99), how many:
```{r}
no.anomalies <- anomalies %>%
  filter(start == -99)

no.anomalies %>% ungroup() %>% dplyr::summarise(n = n_distinct(team))

# 40 teams without anomalies
# 128 - 40 = 88 teams have an anomaly in their average passion
```

```{r}
d <- d %>%
  left_join(anomalies, by = c("team", "m", "mean.pas"))
```
