---
title: 'Anomalies in team passion #2'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(anomaly)
library(tidyverse)
library(skimr)
library(nlme)
library(ggplot2)
library(effects)
library(psych)
```

```{r, message = F, warning = F}
load(file="d.Rdata")
```

Team average passion
```{r}
d <- d %>%
  group_by(pid) %>%
  mutate(m = 1:n()) %>%
  ungroup()

# There are 10 measurements with missings on passion, I delete these 
d <- d %>%
  filter(!is.na(s.pas))

# Team passion average and SD per measurement
d <- d %>%
  group_by(m, team) %>%
  mutate(sd.pas = sd(s.pas, na.rm=TRUE),
         mean.pas = mean(s.pas, na.rm=TRUE)) %>%
  ungroup()
```

```{r}
d_t <-d %>%
  group_by(team, m) %>%
  slice(1) %>%
  ungroup()

df <- d_t[order(d_t$m),] 
df <- df %>%
  select(team, m, mean.pas)
```

Remove teams with no variance (N= 22)
```{r}
df %>%
  group_by(team) %>%
  dplyr::summarise(mad = mad(mean.pas)) %>%
  arrange(mad)

# I remove those teams
df <- df %>%
  group_by(team) %>%
  dplyr::mutate(mad = mad(mean.pas))

df <- df %>%
  filter(mad > 0)

df <- df %>%
  select(-mad)

n_distinct(df$team)
# This leaves 128 teams
```

Function to get anomalies (min length = 3, max length = 9)
```{r, results = "hide", warning = FALSE }
get.an <- function(x) {
  # FOR TESTING:
  # x = df
  # i = 1003
  
  x$start <- NA
  x$end <- NA
  x$section <- NA
  x$mean.change <- NA
  x$test.statistic <- NA
  
  for (i in unique(x$team)) {
    # reset for error handling
    res.capa <- NA
    
    tryCatch({
      res.capa <-
        capa.uv(
          x$mean.pas[x$team == i],
          min_seg_len = 3,
          max_seg_len = 9,
          type = "robustmean"
        )
      res <- collective_anomalies(res.capa)
      cat("Team", i, "has", nrow(res), "anomalous segments.\n")
    }, error = function(e) {
      message("ERROR: Team ", i, ": ", conditionMessage(e))
    })
    
    if (is.na(res.capa)) { # If error detected
      x[x$team == i,] <-
        x %>%
        filter(team == i) %>%
        mutate(start = NaN, # set to NaN to distinguish it from unprocessed or working values
               end = NaN, 
               section = NaN,
               mean.change = NaN)
      
    } else if (nrow(res) > 0) { # If anomaly detected
      
      anomalySection <- mapply(seq, res$start, res$end, SIMPLIFY = FALSE) %>% unlist
      
      x[x$team == i,] <-
        x %>%
        # so that the join doesn't create duplicate columns:
        select(-c("mean.change", "test.statistic")) %>% 
        filter(team == i) %>%
        mutate(start = ifelse(m %in% res$start, 1, 0),
               end = ifelse(m %in% res$end, 1, 0),
               section = ifelse(m %in% anomalySection, cumsum(start), 0)) %>% # cumulative number to indicate number of anomaly periods 
        left_join(res %>% select(-end), by = c('m' = 'start')) #%>%  
        # optionally, uncomment the next line to make the NAs into zeros
        #mutate(across(c("mean.change", "test.statistic"), ~replace_na(.x, 0)))
      
    } else { # If no anomaly detected
      x[x$team == i,] <-
        x %>%
        filter(team == i) %>%
        mutate(start = NA, 
               end = NA, 
               section = NA,
               mean.change = NA, 
               test.statistic = NA)
    }
  }
  return(x)
}

anomalies <- get.an(df) %>% arrange(team)
```

Calculate length of anomalies
```{r}
anomalies <- anomalies %>%
  group_by(team, section) %>%
  mutate(length = n())

anomalies <- anomalies %>%
  mutate(length = ifelse(section > 0, length, NA))
```


Calculate the mean passion score during each anomaly period: 
```{r}
anomalies <- anomalies %>%
  group_by(team) %>%
  mutate(team.mean = mean(mean.pas), # average passion for team across entire period
         anomalies.count = sum(start), # total number of anomalies
         section.mean = ifelse(section == 1, mean(mean.pas[section == 1]), # average passion during anomaly period 1 
                               ifelse(section == 2, mean(mean.pas[section == 2]),
                                      ifelse(section ==3, mean(mean.pas[section == 3]),
                                             ifelse(section ==4, mean(mean.pas[section == 4]),
                                                    ifelse(section ==5, mean(mean.pas[section == 5]),
                                                           ifelse(section == 6, mean(mean.pas[section == 6]), NA))))))) %>%
  ungroup()
```

How many anomalies are there across the teams?
```{r}
anomalies2 <- anomalies %>% group_by(team) %>% slice(1)

anomalies2$anomalies.count[is.na(anomalies2$anomalies.count)] <- 0

table(anomalies2$anomalies.count)
skim(anomalies2$anomalies.count)
```

> On average, teams have 1.74 anomalies

Is the anomaly period a boom (higher than average passion across entire study period) or a bust (lower than average)?
```{r}
# I indicate booms with 2 and busts with 1
anomalies <- anomalies %>%
  mutate(section.bb = ifelse(section.mean > team.mean, 2, # boom = 2
                             ifelse(section.mean < team.mean, 1, 0))) # bust = 1, other = 0

anomalies2 <- anomalies %>%
  mutate(section.bb = ifelse(start == 0, NA, section.bb)) 

anomalies2 <- anomalies2 %>%
  group_by(team)%>%
  add_tally(section.bb[section.bb == 2]) 

anomalies2 <- anomalies2 %>%
  dplyr::rename(boom.count = n)

anomalies2 <- anomalies2 %>%
  group_by(team) %>%
  mutate(boom.count = boom.count / 2)

anomalies2 <- anomalies2 %>%
  group_by(team)%>%
  add_tally(section.bb[section.bb == 1]) 

anomalies2 <- anomalies2 %>%
  dplyr::rename(bust.count = n)
```

How many booms are there?
```{r}
anomalies.b <- anomalies2 %>%
  group_by(team)%>%
  slice(1)%>%
  ungroup()

# Average length of booms
anomalies.b %>%
  filter(section.bb == 2) %>%
  summarise(mean.length = mean(length, na.rm=T),
            sd.length = sd(length),
            min.length = min(length),
            max.length = max(length),
            median.length = median(length))

# Mean length = 4.33, median = 3

table(anomalies.b$boom.count)
skim(anomalies.b$boom.count)
```

How many busts are there?
```{r}
table(anomalies.b$bust.count)

# Average length of busts
anomalies.b %>%
  filter(section.bb == 1) %>%
  summarise(mean.length = mean(length, na.rm=T),
            sd.length = sd(length),
            min.length = min(length),
            max.length = max(length),
            median.length = median(length))

# Mean = 3.88, median = 3

skim(anomalies.b$bust.count)
```

> On average, teams have 0.54 booms (anomaly period with higher passion than the rest of the study) and 1.20 busts (anomaly period with lower passion)

Make two variables to indicate boom and bust instead of one
```{r}
anomalies.data <- anomalies %>%
  mutate(boom = ifelse(section.bb == 2, 1, 0),
         bust = ifelse(section.bb == 1, 1, 0))
```

Also make two variables to indicate the length of booms/busts
```{r}
anomalies.data <- anomalies.data %>%
  mutate(length.boom = ifelse(section.bb == 2, length, NA),
         length.bust = ifelse(section.bb == 1, length, NA))
```

And make dummy variables of these. Booms/busts can be between 3 and 9 measurements long. I recode length of 6 and higher as long (so 6,7,8 or 9) with 2, and below 6 as short (so 3, 4, or 5) with 1, periods with no booms/busts as 0
```{r}
anomalies.data <- anomalies.data %>%
  mutate(length.boom.d = ifelse(length.boom < 6, 1,
                                ifelse(length.boom > 5, 2, 0)),
        length.bust.d = ifelse(length.bust < 6, 1,
                               ifelse(length.bust > 5, 2, 0)))
```

Indicate with the columns after.boom.phase/after.bust.phase if the measurement is after a bust/boom 
```{r}
anomalies.data <- anomalies.data %>%
  mutate(after.boom = ifelse(lag(boom) == 1 & lag(end)== 1, 1, 0),
         after.boom2 = ifelse(lag(after.boom) == 1, 1, 0),
         after.boom3 = ifelse(lag(after.boom2) == 1, 1, 0),
         after.boom4 = ifelse(lag(after.boom3) == 1, 1, 0),
         after.boom.phase = after.boom + after.boom2 + after.boom3 + after.boom4) %>%
  select(-c(after.boom, after.boom2, after.boom3, after.boom4))

anomalies.data <- anomalies.data %>%
  mutate(after.bust = ifelse(lag(bust) == 1 & lag(end)== 1, 1, 0),
         after.bust2 = ifelse(lag(after.bust) == 1, 1, 0),
         after.bust3 = ifelse(lag(after.bust2) == 1, 1, 0),
         after.bust4 = ifelse(lag(after.bust3) == 1, 1, 0),
         after.bust.phase = after.bust + after.bust2 + after.bust3 + after.bust4) %>%
  select(-c(after.bust, after.bust2, after.bust3, after.bust4))

anomalies.data <- anomalies.data %>% 
  mutate(after.boom.phase2 = ifelse(after.boom.phase == 1, 1, 
                                    ifelse(boom == 1, 0, NA))) %>%
  select(-c(after.boom.phase))

anomalies.data <- anomalies.data %>% 
  mutate(after.bust.phase2 = ifelse(after.bust.phase == 1, 1, 
                                    ifelse(bust == 1, 0, NA))) %>%
  select(-c(after.bust.phase))
    
anomalies.data <- anomalies.data %>% 
  dplyr::rename(after.boom.phase = after.boom.phase2,
                after.bust.phase = after.bust.phase2)



```

Create a dummy to indicate if the measurement is after a long or short boom/bust
This is the column after.boom.length.d or after.bust.length.d (2 = after long one, 1 is after short one, 0 = during boom/bust)
```{r}
anomalies.data <- anomalies.data %>%
  mutate(after.boom.d = ifelse(lag(length.boom.d) == 2 & lag(end) == 1, 2,
                               ifelse(lag(length.boom.d) == 1 & lag(end) == 1, 1, 0)),
         after.boom.d2 = ifelse(lag(after.boom.d) == 2, 2,
                                ifelse(lag(after.boom.d) == 1, 1, 0)),
         after.boom.d3 = ifelse(lag(after.boom.d2) == 2, 2,
                                ifelse(lag(after.boom.d2) == 1, 1, 0)),
         after.boom.d4 = ifelse(lag(after.boom.d3) == 2, 2,
                                ifelse(lag(after.boom.d3) == 1, 1, 0)),
         after.boom.length.d = after.boom.d + after.boom.d2 + after.boom.d3 + after.boom.d4) %>%
  select(-c(after.boom.d, after.boom.d2, after.boom.d3, after.boom.d4))

anomalies.data <- anomalies.data %>%
  mutate(after.boom.length.d = ifelse(is.na(after.boom.phase), NA, after.boom.length.d))

anomalies.data <- anomalies.data %>%
  mutate(after.bust.d = ifelse(lag(length.bust.d) == 2 & lag(end) == 1, 2,
                               ifelse(lag(length.bust.d) == 1 & lag(end) == 1, 1, 0)),
         after.bust.d2 = ifelse(lag(after.bust.d) == 2, 2,
                                ifelse(lag(after.bust.d) == 1, 1, 0)),
         after.bust.d3 = ifelse(lag(after.bust.d2) == 2, 2,
                                ifelse(lag(after.bust.d2) == 1, 1, 0)),
         after.bust.d4 = ifelse(lag(after.bust.d3) == 2, 2,
                                ifelse(lag(after.bust.d3) == 1, 1, 0)),
         after.bust.length.d = after.bust.d + after.bust.d2 + after.bust.d3 + after.bust.d4) %>%
  select(-c(after.bust.d, after.bust.d2, after.bust.d3, after.bust.d4))

anomalies.data <- anomalies.data %>%
  mutate(after.bust.length.d = ifelse(is.na(after.bust.phase), NA, after.bust.length.d))
```

Save
```{r}
save(anomalies.data, file = "anomalies.data.Rdata")
```

# Join with individual-level data
```{r}
d.an <- d %>%
  left_join(anomalies.data, by = c("team", "m", "mean.pas"))

# This makes that only the first measurement occassion of the bust/boom is coded  
d.an.first <- d.an %>%
  mutate(boom = ifelse(section.bb == 2 & start == 1, 1, 0),
         bust = ifelse(section.bb == 1 & start == 1, 1, 0))

# Replace na with zero
d.an.first$boom[is.na(d.an.first$boom)] <- 0
d.an.first$bust[is.na(d.an.first$bust)] <- 0
d.an.first$length.boom[is.na(d.an.first$length.boom)] <- 0

# This makes that only the last measurement occassion of the bust/boom is coded  
d.an.last <- d.an %>%
  mutate(boom = ifelse(section.bb == 2 & end == 1, 1, 0),
         bust = ifelse(section.bb == 1 & end == 1, 1, 0))

# Replace na with zero
d.an.last$boom[is.na(d.an.last$boom)] <- 0
d.an.last$bust[is.na(d.an.last$bust)] <- 0
d.an.last$length.boom[is.na(d.an.last$length.boom)] <- 0
d.an.last$length.bust[is.na(d.an.last$length.bust)] <- 0

d.an.an <- d.an

# Not replacing NAs with zeroes
save(d.an.an, file = "d.an.an.Rdata")

# Replace na with zero
d.an$boom[is.na(d.an$boom)] <- 0
d.an$bust[is.na(d.an$bust)] <- 0
d.an$length.boom[is.na(d.an$length.boom)] <- 0
d.an$length.bust[is.na(d.an$length.bust)] <- 0

```

Save
```{r}
save(d.an, file="d.an.Rdata")
save(d.an.first, file = "d.an.first.Rdata")
save(d.an.last, file = "d.an.last.Rdata")
```

