---
title: "Changes in residual variance over time"
output: github_document
---

> The emergence of consensus (or the opposite, increases in divergence) can be captured by modeling changes in residual variances over time in multilevel growth models.

> A two-level model estimates this through including (1) a time variable that accounts for change in the group means over time and (2) a variance function to account for changes in the residual variance over time.

> See also Lang et al. 2019 (http://dx.doi.org/10.1037/0000115-023) 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(tidyverse)
library (nlme)
```

Step 0: Add time variable (= measurement count)
```{r, message = F, warning = F}
load("d.Rdata")

d <- d %>%
  select(team, pid, day, type, s.pas)

d$team <- as.factor(d$team)
d$pid <- as.factor(d$pid)

d <- d[with(d, order(pid, day, type)),]

d <- d %>%
  group_by(pid) %>%
  mutate(m = 1:n()) %>%
  ungroup()
```


Step 1: Examine change in groups' latent means over time, i.e. does group-level passion increase or decrease over time? 
```{r, message = F, warning = F}
step1 <- lme(s.pas ~ m, random =
             list(team = pdDiag(~1), pid = pdSymm(~1)),
           data = d, na.action = na.omit)

summary(step1)
VarCorr(step1)
```
> Average passion for work decreases slightly over time

Step 2: Do some teams increase or decrease more in passion over time than the average, i.e. examining slope variability
```{r, message = F, warning = F}
step2a <-update(step1, random = list(team = pdDiag(~m), pid=pdSymm(~1)))
summary(step2a)
VarCorr(step2a)

step2b <-update(step2a, random = list(team = pdSymm(~m), pid=pdSymm(~1)), 
                control = lmeControl(opt = "optim"))

summary(step2b)
VarCorr(step2b)

anova(step1, step2a, step2b)
```
> Including a random slope improves the model fit, which suggests that there is variability between groups in group-level passion change over time.

Step 3: Is there an increase or decrease in passion consensus within groups? I.e. do group members' passion levels become more or less homogeneous over time?
```{r, message = F, warning = F}
step3 <- update(step2b, weights = varExp( form = ~ m))

anova(step1, step2a, step2b, step3)
summary(step3)$tTable

VarCorr(step3)

summary(step3)$modelStruct$varStruct
```

> The error term estimated in the last step reflects the percentage increase in the standard deviation of the errors with each unit increase in the time variable. 

> So the residual variance at measurement 0 = 1.59 * (1.59 * exp[2 * 0.0013 * 0]) = 2.5281

> The residual variance at measurement 60 = 1.59 * (1.59 * exp[2 * 0.0013 * 60]) = 2.95491

> In other words, over the whole study period, team members become less similar to each other in how passionate they are (!)

```{r, message = F, warning = F}

```

```{r, message = F, warning = F}

```

