---
title: "CRRC passion predicted by difference in own experience - team perception"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=F}
library(dplyr)
library(psych)
library(nlme)
library(ggplot2)
library(effects)
library(correlation)
```

```{r, message=F}
load("/Volumes/Anne/Harvard/Teams/Teams/d.Rdata")
```

### How does the difference between self- and other report stress at current moment predict passion for work at next moment? 

Create lead variable for passion and difference scores (i.e. next moment - current moment)
```{r, message=F}
d <- d[with(d, order(pid, day, type)),]

d <- d %>%
  group_by(pid) %>%
  mutate(s.pas.lead = lead(s.pas, n=1L)) %>%
  mutate(s.pas.diff = s.pas.lead - s.pas) %>%
  ungroup()
```

Stress perceived by team members (o.em1)
```{r}
d <- d %>%
  group_by(pid, day, type) %>%
    mutate(stress.av = mean(c(o.em1_1, o.em1_2, o.em1_3, o.em1_4, o.em1_5, o.em1_6, o.em1_7), na.rm=T))

d$stress.av[is.nan(d$stress.av)]<-NA
```  

Create stress_av lead, this leads the stress_av variable with 1 measurement occasion because other report about the morning is collected in the afternoon, and other report about the afternoon is collected in the evening. 
```{r}
d <- d[with(d, order(pid, day, type)),]

d <- d %>%
  group_by(pid) %>%
  mutate(stress.av.lead = lead(stress.av, n=1L)) %>%
  ungroup()

```

Calculate difference between self-reported stress and other reported stress
```{r}
# If stress.diff is positive, this means that I am more stressed than team members think I am
d <- d %>%
  mutate(stress.diff = s.em1 - stress.av, na.rm=T)
```

Correlation between self- and other reported stress at time t and passion for work at time t+1
```{r}
# Self-report
d %>%
  select(s.em1, s.pas.lead) %>%
  correlation()

d %>%
  ggplot(aes(x=s.pas.lead, y=s.em1)) + 
  geom_jitter() +
  geom_smooth(method="lm", se=F)

# Other report
d %>%
  select(stress.av.lead, s.pas.lead) %>%
  correlation()

d %>%
  ggplot(aes(x=s.pas.lead, y=stress.av.lead)) + 
  geom_jitter() +
  geom_smooth(method="lm", se=F)

# Difference between self-report and other report
d %>%
  select(stress.diff, s.pas.lead) %>%
  correlation()

d %>%
  ggplot(aes(x=s.pas.lead, y=stress.diff)) + 
  geom_jitter() +
  geom_smooth(method="lm", se=F)
```
Multilevel model, persons nested in teams, passion at time t+1 predicted by the self-other report discrepancy
```{r}
# Random intercept for team and id
model1 <- lme(fixed = s.pas.lead ~ stress.diff,
              random = ~1 | tid/pid,
              data = d,
              na.action = na.omit)

summary(model1)

# Random slopes for team and id
model2 <- lme(fixed = s.pas.lead ~ stress.diff,
              random = ~ stress.diff | tid/pid,
              data = d,
              na.action = na.omit)

summary(model2)
```

### How does the difference between self-reported happiness and team-reported happiness associate with passion over time?

Happiness perceived by team members (o.em2)
```{r}
d <- d %>%
  group_by(pid, day, type) %>%
    mutate(hap.av = mean(c(o.em2_1, o.em2_2, o.em2_3, o.em2_4, o.em2_5, o.em2_6, o.em2_7), na.rm=T))

d$hap.av[is.nan(d$hap.av)]<-NA
```  

Create hap.av lead (same thing as for stress.av). 
```{r}
d <- d[with(d, order(pid, day, type)),]

d <- d %>%
  group_by(pid) %>%
  mutate(hap.av.lead = lead(hap.av, n=1L)) %>%
  ungroup()
```

Calculate difference between self-reported happiness and other reported happiness
```{r}
# If hap.diff is positive, this means that I am happier than team members think I am
d <- d %>%
  mutate(hap.diff = s.em2 - hap.av, na.rm=T)
```

Correlation between self- and other reported happiness at time t and passion for work at time t+1
```{r}
# Self-report
d %>%
  select(s.em2, s.pas.lead) %>%
  correlation()

d %>%
  ggplot(aes(x=s.pas.lead, y=s.em2)) + 
  geom_jitter() +
  geom_smooth(method="lm", se=F)

# Other report
d %>%
  select(hap.av.lead, s.pas.lead) %>%
  correlation()

d %>%
  ggplot(aes(x=s.pas.lead, y=hap.av.lead)) + 
  geom_jitter() +
  geom_smooth(method="lm", se=F)

# Difference between self-report and other report
d %>%
  select(hap.diff, s.pas.lead) %>%
  correlation()

d %>%
  ggplot(aes(x=s.pas.lead, y=hap.diff)) + 
  geom_jitter() +
  geom_smooth(method="lm", se=F)
```

Multilevel model, persons nested in teams, passion at time t+1 predicted by the self-other report discrepancy
```{r}
# Random intercept for team and id
model3 <- lme(fixed = s.pas.lead ~ hap.diff,
              random = ~1 | tid/pid,
              data = d,
              na.action = na.omit)

summary(model3)

# Random slopes for team and id
model4 <- lme(fixed = s.pas.lead ~ hap.diff,
              random = ~ hap.diff | tid/pid,
              data = d,
              na.action = na.omit)

summary(model4)
```

```{r}


```





