---
title: "During booms/busts: stress, burnout, feeling connected, interactions, and social behavior"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(anomaly)
library(tidyverse)
library(skimr)
library(nlme)
library(ggplot2)
library(effects)
library(psych)
```

```{r, message = F, warning = F}
load(file="d.an.Rdata")
```

## Stress during boom/busts compared to other times

s.jd1	This afternoon, very few stressful things happened to me at work.
```{r}
## Boom
model_1 <- lme(fixed = s.jd1 ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit)

summary(model_1)

# Bust
model_1b <- lme(fixed = s.jd1 ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit) 

summary(model_1b)
```

> During booms, participants agreed more with 'very few stressful things happened'. During busts, less agreement

s.b2	How burned out do you feel right now?
```{r}
## Boom
model_2 <- lme(fixed = s.b2 ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit)

summary(model_2)

# Bust
model_2b <- lme(fixed = s.b2 ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit) 

summary(model_2b)
```

> Participants felt less burned out during booms and more during busts

s.jd2	This afternoon, I felt bothered or upset because of my job.
```{r}
## Boom
model_3 <- lme(fixed = s.jd2 ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_3)

# Bust
model_3b <- lme(fixed = s.jd2 ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_3b)
```

> Participants felt less bothered by things during booms and more during busts

s.jd3	This afternoon, I felt a great deal of stress because of my job.
```{r}
## Boom
model_4 <- lme(fixed = s.jd3 ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_4)

# Bust
model_4b <- lme(fixed = s.jd3 ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_4b)
```

> Participants felt less stressed during booms and more stressed during busts

s.jd4	This afternoon, I was under constant time pressure due to a heavy workload.
```{r}
## Boom
model_5 <- lme(fixed = s.jd4 ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_5)

# Bust
model_5b <- lme(fixed = s.jd4 ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_5b)
```

> Participants felt less time pressured during booms and more during busts

## Interactions with team-mates during booms/busts

s.ip	Please circle all of the teammates who you interacted with this afternoon.
Total = s.ip_1 + s.ip_2 + s.ip_3 + s.ip_4 + s.ip_5 + s.ip_6 + s.ip_7
```{r}
d.an <- d.an %>%
  dplyr::mutate(s.ip.t = rowSums(across(c(s.ip_1, s.ip_2, s.ip_3, s.ip_4, s.ip_5, s.ip_6, s.ip_7)), na.rm=T))
                
## Boom
model_6 <- lme(fixed = s.ip.t ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_6)

# Bust
model_6b <- lme(fixed = s.ip.t ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_6b)
```

> Participants did not interact with more or fewer team mates during booms/busts

s.il	Approximately how many minutes did you spend in interactions with each team member this afternoon?
```{r}
# Total number of minutes
d.an <- d.an %>%
  dplyr::mutate(s.il.t = rowSums(across(c(s.il_1, s.il_2, s.il_3, s.il_4, s.il_5, s.il_6, s.il_7)), na.rm=T))

# There are some participants who said they didn't interact with anyone (s.ip.t = 0) but nonetheless said they interacted X number of minutes in total. I set the number of minutes to 0 for these participants (78 measurements). 

d.an <- d.an %>%
  mutate(s.il.t = ifelse(s.ip.t == 0, 0, s.il.t))

# Mean number of minutes per team mate
d.an <- d.an %>%
  dplyr::mutate(s.il.m = s.il.t / s.ip.t)

d.an$s.il.m[is.na(d.an$s.il.m)] <- 0 

## Boom
model_7 <- lme(fixed = s.il.m ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_7)

# Bust
model_7b <- lme(fixed = s.il.m ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_7b)
```

> Participants had longer interactions during booms and even longer interactions during busts

s.ie	How much did you enjoy interacting with each team member this afternoon? 
```{r}
# Total enjoyment
d.an <- d.an %>%
  dplyr::mutate(s.ie.t = rowSums(across(c(s.ie_1, s.ie_2, s.ie_3, s.ie_4, s.ie_5, s.ie_6, s.ie_7)), na.rm=T))

# There are some participants who said they didn't interact with anyone (s.ip.t = 0) but nonetheless said they enjoyed the interaction. I set the number of minutes to 0 for these participants (78 measurements). 

d.an <- d.an %>%
  mutate(s.ie.t = ifelse(s.ip.t == 0, 0, s.ie.t))

# Mean number of minutes per team mate
d.an <- d.an %>%
  dplyr::mutate(s.ie.m = s.ie.t / s.ip.t)

d.an$s.ie.m[is.na(d.an$s.ie.m)] <- 0 

## Boom
model_8 <- lme(fixed = s.ie.m ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_8)

# Bust
model_8b <- lme(fixed = s.ie.m ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_8b)
```

> Participants enjoyed interactions more during booms and less during busts

## Social behavior: how rude, kind, gregarious, and talkative were participants during booms/busts?

s.ps1	How rude were you to your teammates this morning/afternoon?
```{r}
## Boom
model_9 <- lme(fixed = s.ps1 ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_9)

# Bust
model_9b <- lme(fixed = s.ps1 ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_9b)
```

> Participants were less rude to team mates during booms and more during busts

s.ps2	How gregarious were you around your teammates this morning?
```{r}
## Boom
model_10 <- lme(fixed = s.ps2 ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_10)

# Bust
model_10b <- lme(fixed = s.ps2 ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_10b)
```

> Participants were more gregarious to team mates during booms and less during busts

s.ps3	How kind, considerate were you to your teammates this morning? 
```{r}
## Boom
model_11 <- lme(fixed = s.ps3 ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_11)

# Bust
model_11b <- lme(fixed = s.ps3 ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_11b)
```

> Participants were more kind and considerate to team mates during booms and less during busts

s.ps4	How talkative were you around your teammates this morning?
```{r}
## Boom
model_12 <- lme(fixed = s.ps4 ~ boom,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim"))

summary(model_12)

# Bust
model_12b <- lme(fixed = s.ps4 ~ bust,
                   random = ~1 | team/pid, 
                   data = d.an, 
                   na.action = na.omit, control = lmeControl(opt = "optim")) 

summary(model_12b)
```

> Participants were more talkative during booms and less during busts

s.c	How connected do you feel with the people on your team right now? 
s.b2	How burned out do you feel right now?
s.jd1	This afternoon, very few stressful things happened to me at work.
s.jd2	This afternoon, I felt bothered or upset because of my job.
s.jd3	This afternoon, I felt a great deal of stress because of my job.
s.jd4	This afternoon, I was under constant time pressure due to a heavy workload.


s.ps1	How rude were you to your teammates this morning?
s.ps2	How gregarious were you around your teammates this morning?
s.ps3	How kind, considerate were you to your teammates this morning? 
s.ps4	How talkative were you around your teammates this morning?


s.ip	Please circle all of the teammates who you interacted with this afternoon.
Total = s.ip_1 + s.ip_2 + s.ip_3 + s.ip_4 + s.ip_5 + s.ip_6 + s.ip_7
s.im	How did you primarily interact with each team member this afternoon?
s.il	Approximately how many minutes did you spend in interactions with each team member this afternoon?
s.ie	How much did you enjoy interacting with each team member this afternoon? 