---
title: "Passion interaction SD and mean"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999) 
```

```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(tidyverse)
library(nlme)
library(lattice)
library(skimr)
library(ggplot2)
library(effects)
library(relativeVariability)
library(multilevel)
library(tidyr)
library(psych)
library(ggpubr)
```

## Prep

Create measurement indicator (m) and calculate within-team average (mean.pas) and standard deviation (sd.pas) of passion (on each measurement occasion). Calculate also average per day (mean.pas.d) and sd per day (sd.pas.d). Create week-indicator (week)
```{r, message = F, warning = F}
load(file="d.Rdata")

d <- d[with(d, order(pid, day, type)),]

d <- d %>%
  group_by(pid) %>%
  mutate(m = 1:n()) %>%
  ungroup()

d$team <- as.factor(d$team)
d$pid <- as.factor(d$pid)

# There are 10 measurements with missings on passion, I delete these 
d <- d %>%
  filter(!is.na(s.pas))

d <- d %>%
  group_by(team, m) %>%
  mutate(sd.pas = sd(s.pas),
         mean.pas = mean(s.pas)) %>%
  ungroup()

# Passion SD and mean
d <- d %>%
  group_by(team, day) %>%
  mutate(sd.pas.d = sd(s.pas),
         mean.pas.d = mean(s.pas)) %>%
  ungroup()

# Week indicator
d <- d %>%
  mutate(week = case_when(
    day > 0 & day < 8 ~ 1,
    day > 7 & day < 15 ~2,
    day > 14 & day < 22 ~3))

# New day variable to indicate day of the week (1,2,3,4,5,6,7, 1,2,3,4,5,6,7 etc)
d <- d %>%
  mutate(day.new = case_when(
    day == 1 | day == 8 | day == 15 ~ 1,
    day == 2 | day == 9 | day == 16 ~ 2,
    day == 3 | day == 10 | day == 17 ~ 3,
    day == 4 | day == 11 | day == 18 ~ 4,
    day == 5 | day == 12 | day == 19 ~ 5,
    day == 6 | day == 13 | day == 20 ~ 6,
    day == 7 | day == 14 ~ 7))
```

## Predicting emotional exhaustion

Predicting emotional exhaustion (evening) from the interaction between daily team passion mean and SD:
```{r}
model_1 <- lme(fixed = s.ee ~ sd.pas.d + mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d, 
                   na.action = na.omit)

summary(model_1)

# Interaction
model_1b <- lme(fixed = s.ee ~ sd.pas.d + mean.pas.d + sd.pas.d*mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d, 
                   na.action = na.omit)

summary(model_1b)

# Likelihood check
model_1r <- lme(fixed = s.ee ~ sd.pas.d + mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d, 
                   na.action = na.omit, method = "ML")

model_1br <- lme(fixed = s.ee ~ sd.pas.d + mean.pas.d + sd.pas.d*mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d, 
                   na.action = na.omit, method = "ML")

anova(model_1r, model_1br)
```

Plotting the interaction between passion SD and mean for higher and lower levels of the mean (+ and -2 SD)
```{r}
describe(d$mean.pas.d)
#sd = 0.94 --> 2*0.94 = 1.88

eff <- effect("sd.pas.d:mean.pas.d", xlevels = list(mean.pas.d = c(-1.88, 1.88)), model_1b)

effdata <- as.data.frame(eff)

effdata$mean.pas.d <- as.factor(effdata$mean.pas.d)

plot <- ggplot(effdata, aes(x = sd.pas.d, y = fit, color = mean.pas.d, group = mean.pas.d)) +
  geom_point() +
  geom_line(size = 1.2) + 
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=mean.pas.d),alpha=0.3) +
  labs(title = "Emotional exhaustion from team passion", x= "Within-team passion SD", y="Emotional exhaustion (individual)", color="Team passion intensity", fill="Team passion intensity") + theme_classic() + theme(text=element_text(size=12)) + 
  scale_fill_discrete(labels = c("mean -2SD", "mean + 2SD")) +   scale_color_discrete(labels = c("mean -2SD", "mean + 2SD"))

```

```{r}
plot
```
## Next morning stress and burnout

```{r}
d <- d %>%
  mutate(stress.m = lead(s.em1, n=1L),
         burnout.m = lead(s.b2, 1L))

# Select only evening measurements (doesn't matter for average team passion/sd but does for stress)

d2 <- d %>%
  filter(type == "e")
```

Models for stress:
```{r}
model_2 <- lme(fixed = stress.m ~ sd.pas.d + mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d2, 
                   na.action = na.omit)

summary(model_2)

# Interaction
model_2b <- lme(fixed = stress.m ~ sd.pas.d + mean.pas.d + sd.pas.d*mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d2, 
                   na.action = na.omit)

summary(model_2b)

# Likelihood check
model_2r <- lme(fixed = stress.m ~ sd.pas.d + mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d2, 
                   na.action = na.omit, method = "ML")

model_2br <- lme(fixed = stress.m ~ sd.pas.d + mean.pas.d + sd.pas.d*mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d2, 
                   na.action = na.omit, method = "ML")

anova(model_2r, model_2br)
```

> Best model is model without interaction effect

Plots for stress:
```{r}
eff1 <- effect(c("sd.pas.d"),  model_2)
eff2 <- effect(c("mean.pas.d"),  model_2)

effdata1 <- as.data.frame(eff1)
effdata2 <- as.data.frame(eff2)

plot1 <- ggplot(effdata1, aes(x = sd.pas.d, y = fit)) +
  geom_point() +
  geom_line(size = 1.2) + 
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se),alpha=0.3) +
  labs(x= "Within-team passion SD", y="Stress (morning)") + theme_classic() + theme(text=element_text(size=12)) 

plot2 <- ggplot(effdata2, aes(x = mean.pas.d, y = fit)) +
  geom_point() +
  geom_line(size = 1.2) + 
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se),alpha=0.3) +
  labs(x= "Within-team passion mean", y="Stress (morning)") + theme_classic() + theme(text=element_text(size=12)) 

library(ggpubr)

plots <- ggarrange(plot1, plot2, ncol = 2, nrow = 1)
plots <- annotate_figure(plots, top = text_grob("Next morning stress from team passion mean and SD"))

plots
```
Models for burnout
```{r}
model_3 <- lme(fixed = burnout.m ~ sd.pas.d + mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d2, 
                   na.action = na.omit)

summary(model_3)

# Interaction
model_3b <- lme(fixed = burnout.m ~ sd.pas.d + mean.pas.d + sd.pas.d*mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d2, 
                   na.action = na.omit)

summary(model_3b)

# Likelihood check
model_3r <- lme(fixed = burnout.m ~ sd.pas.d + mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d2, 
                   na.action = na.omit, method = "ML")

model_3br <- lme(fixed = burnout.m ~ sd.pas.d + mean.pas.d + sd.pas.d*mean.pas.d,
                   random = ~1 | team/pid, 
                   data = d2, 
                   na.action = na.omit, method = "ML")

anova(model_3r, model_3br)
```
> The model without the interaction is best but there are main effects for the meand and SD

Plots for burnout:
```{r}
eff1 <- effect(c("sd.pas.d"),  model_3)
eff2 <- effect(c("mean.pas.d"),  model_3)

effdata1 <- as.data.frame(eff1)
effdata2 <- as.data.frame(eff2)

plot1 <- ggplot(effdata1, aes(x = sd.pas.d, y = fit)) +
  geom_point() +
  geom_line(size = 1.2) + 
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se),alpha=0.3) +
  labs(x= "Within-team passion SD", y="Burnout (morning)") + theme_classic() + theme(text=element_text(size=12)) 

plot2 <- ggplot(effdata2, aes(x = mean.pas.d, y = fit)) +
  geom_point() +
  geom_line(size = 1.2) + 
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se),alpha=0.3) +
  labs(x= "Within-team passion mean", y="Burnout (morning)") + theme_classic() + theme(text=element_text(size=12)) 

plots <- ggarrange(plot1, plot2, ncol = 2, nrow = 1)
plots <- annotate_figure(plots, top = text_grob("Next morning burnout from team passion mean and SD"))

plots
```

```{r}

```
