---
title: "Predicting future burnout from passion"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(tidyverse)
library(nlme)
library(lattice)
library(skimr)
library(ggplot2)
library(effects)
```
Create variable "post" that indicates if measurement occurred after maximum team-level passion (team average) was reached (post = 1 if measurement is after, 0 = measurement is before)
```{r, message = F, warning = F}
load(file="d.Rdata")

d <- d[with(d, order(pid, day, type)),]

d <- d %>%
  group_by(pid) %>%
  mutate(m = 1:n()) %>%
  ungroup()

d$team <- as.factor(d$team)
d$pid <- as.factor(d$pid)

d <- d %>%
  filter(!is.na(s.pas))

d <- d %>%
  group_by(team, m) %>%
  mutate(sd.pas = sd(s.pas),
         mean.pas = mean(s.pas)) %>%
  ungroup()

# max = 0 if mean.pas = maximum
d2 <- d %>%
  group_by(team) %>%
  mutate(max = ifelse(mean.pas == max(mean.pas), 0, 1))

# First measurement on which maximum passion was reached
d3 <- d2 %>%
  group_by(team) %>%
  arrange(max, m) %>%
  slice(1) %>%
  ungroup()

d3 <- d3 %>%
  mutate(firstm = m) %>%
  select(pid, m, firstm)

# Merge with original data
d4 <- d2 %>%
  left_join(d3, by = c("pid", "m"))

d5 <- d4 %>%
  group_by(team) %>%
  fill(firstm, .direction = "downup")

# post = 1 if measurement (m) is after the measurement on which maximum average passion was reached
d6 <- d5 %>%
  group_by(team) %>%
  mutate(post = ifelse(m > firstm, 1, 0)) 

d7 <- d6 %>%
  select(c(pid, m, post))

# Join with original data
d8 <- d %>%
  left_join(d7, by = c("pid", "m"))

d <- d8

d$post <- as.factor(d$post)

d<- d%>%
  dplyr::rename(team = team.x)
```

Centering s.pas on team level
```{r}
d.c <- d %>%
  mutate(s.pas.dev = s.pas -mean.pas)
```

Create lead (= next moment) variable of burnout 
```{r}
d.c <- d.c[with(d.c, order(day, type, pid)),]

d.c <- d.c %>%
  group_by(pid) %>%
  mutate(s.b2.lead = lead(s.b2, n=1L))
```

## Predicting burn-out from passion

Multilevel model predicting burnout at next measurement occasion from current passion level --> passion as deviation from team-level mean. This answers the question: do I feel more/less burnout after if I'm more/less passionate than my team? Multilevel model with random intercepts.
```{r}
model_1 <- lme(fixed = s.b2.lead ~ s.pas.dev,
                   random = ~1 | team/pid, 
                   data = d.c, 
                   na.action = na.omit,
                   control = lmeControl(opt = "optim"))

summary(model_1)
```

Include average team-level passion
```{r}
model_2 <- lme(fixed = s.b2.lead ~ mean.pas + s.pas.dev,
                   random = list(team = ~1, pid = ~1), 
                   data = d.c, 
                   na.action = na.omit)

summary(model_2)

anova(model_1, model_2)
```

Does this depend on whether it occurs before or after a peak in team-level passion? 
```{r}
model_3 <- lme(fixed = s.b2.lead ~ mean.pas + s.pas.dev + post + s.pas.dev*post,
                   random = list(team = ~1, pid = ~1), 
                   data = d.c, 
                   na.action = na.omit)

summary(model_3)

anova(model_2, model_3)
```
Including the post-peak dummy does not change the model fit so we should leave these predictors out.  

Model 2 + random slopes for s.pas.dev at id level.
```{r}
model_4 <- lme(fixed = s.b2.lead ~ mean.pas + s.pas.dev,
                   random = list(team = ~1, pid = ~s.pas.dev),
                   data = d.c, 
                   na.action = na.omit)

summary(model_4)

anova(model_2, model_4)
```

Model with random slopes for s.pas.dev at id level and team level.
```{r}
model_5 <- lme(fixed = s.b2.lead ~ mean.pas + s.pas.dev,
                   random = list(team = ~s.pas.dev, pid = ~s.pas.dev),
                   data = d.c, 
                   na.action = na.omit)

summary(model_5)

anova(model_4, model_5)
```
Model with random slope at id-level seems better (model 4). 

> Results suggest that a positive deviation from average team passion levels predicts lower burnout at the next measurement occasion. Also, average team level passion is associated with lower burnout at the next measurement. 

Plot of predicted values
```{r}
eff <- effect("s.pas.dev", model_4)

plotje <- ggplot(as.data.frame(eff),
                 aes(s.pas.dev, fit)) +
  geom_line() +
  geom_errorbar(aes(ymin = fit-se, ymax = fit+se), width = 1)

```

