---
title: 'Predicting passion variance over time #2'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(tidyverse)
library(nlme)
library(lattice)
library(skimr)
library(ggplot2)
library(effects)
library(relativeVariability)
library(multilevel)
```

## Prep

Create measurement indicator (m) and calculate within-team average (mean.pas) and standard deviation (sd.pas) of passion (on each measurement occasion): 
```{r, message = F, warning = F}
load(file="d.Rdata")

d <- d[with(d, order(pid, day, type)),]

d <- d %>%
  group_by(pid) %>%
  mutate(m = 1:n()) %>%
  ungroup()

d$team <- as.factor(d$team)
d$pid <- as.factor(d$pid)

# There are 10 measurements with missings on passion, I delete these 
d <- d %>%
  filter(!is.na(s.pas))

d <- d %>%
  group_by(team, m) %>%
  mutate(sd.pas = sd(s.pas),
         mean.pas = mean(s.pas)) %>%
  ungroup()
```

We want to look at SD variability across days, so I recode the daytime indicator (type) into 1,2,3
```{r}
d$type <- as.factor(d$type)
levels(d$type)

# They are ordered afternoon, evening, morning

levels(d$type) <- c("2", "3", "1")

d$type <- as.numeric(d$type)
```

## Predicting within-day SD variability 

Three-level multilevel model (teams/participants/day), although maybe it should be a four-level model? 
```{r}
# Random intercept (+ correcting for the mean)
model_1 <- lme(fixed = sd.pas ~ type + mean.pas,
                   random = ~1 | team/pid/day, 
                   data = d, 
                   na.action = na.omit)

summary(model_1)

# Random slope for type on team and participant level
model_1b <- lme(fixed = sd.pas ~ type + mean.pas,
                   random = list(team = ~type, pid = ~type, day = ~1), 
                   data = d, 
                   na.action = na.omit)

summary(model_1b)

# Compare likelihoods (using ML instead of REML, otherwise likelihoods are not comparable)
model_1r <- lme(fixed = sd.pas ~ type + mean.pas,
                   random = ~1 | team/pid/day, 
                   data = d, 
                   na.action = na.omit, method = "ML")

model_1br <- lme(fixed = sd.pas ~ type + mean.pas,
                   random = list(team = ~type, pid = ~type, day = ~1), 
                   data = d, 
                   na.action = na.omit, method = "ML")

anova(model_1r, model_1br)

# Second model including random slopes for team and pid is better
# Adding random slope for day 

# Random slope for day on team and participant and day level
model_1c <- lme(fixed = sd.pas ~ type + mean.pas,
                   random = list(team = ~type, pid = ~type, day = ~type), 
                   data = d, 
                   na.action = na.omit)

summary(model_1c)

model_1cr <- lme(fixed = sd.pas ~ type + mean.pas,
                   random = list(team = ~type, pid = ~type, day = ~type), 
                   data = d, 
                   na.action = na.omit, method = "ML")

anova(model_1br, model_1cr)

# Best model is model with random slopes for team and participants. In this model there is no significant change in SD over the course of the day
```

## Using the relative standard deviation

Relative variability index >>> this is a measure of variability that is not confounded by the mean. See also Mestdagh et al. (2018, http://dx.doi.org/10.1037/met0000153). 
```{r}
# Calculate relative variability rl.sd
rel.sd <- function(x) {
  relativeSD(x, MIN = 1, MAX=7)
}

d2 <- d %>%
  group_by(team, m) %>%
  mutate(rl.sd = rel.sd(s.pas))

```

Predicting within-team passion variance over time using the relative sd.
```{r}
# Random intercept
model_2 <- lme(fixed = rl.sd ~ type,
                   random = ~1 | team/pid/day, 
                   data = d2, 
                   na.action = na.omit)

summary(model_2)

# Random slopes for team and pid
model_2b <- lme(fixed = rl.sd ~ type,
                    random = list(team = ~type, pid = ~type, day = ~1), 
                   data = d2, 
                   na.action = na.omit)

summary(model_2b)

# Check likelihoods
model_2r <- lme(fixed = rl.sd ~ type,
                   random = ~1 | team/pid/day, 
                   data = d2, 
                   na.action = na.omit, method = "ML")

model_2br <- lme(fixed = rl.sd ~ type,
                   random = list(team = ~type, pid = ~type, day = ~1), 
                   data = d2, 
                   na.action = na.omit, method = "ML")

anova(model_2r, model_2br)

# Second model is better. In this model there is also no change in SD over the days
```

