---
title: "Predicting passion variance over time"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message = F, warning = F}
library(knitr)
library(dplyr)
library(tidyverse)
library(nlme)
library(lattice)
library(skimr)
library(ggplot2)
library(effects)
library(relativeVariability)
library(multilevel)
```
## Prep

Create measurement indicator (m) and calculate within-team average (mean.pas) and standard deviation (sd.pas) of passion: 
```{r, message = F, warning = F}
load(file="d.Rdata")

d <- d[with(d, order(pid, day, type)),]

d <- d %>%
  group_by(pid) %>%
  mutate(m = 1:n()) %>%
  ungroup()

d$team <- as.factor(d$team)
d$pid <- as.factor(d$pid)

# There are 10 measurements with missings on passion, I delete these 
d <- d %>%
  filter(!is.na(s.pas))

d <- d %>%
  group_by(team, m) %>%
  mutate(sd.pas = sd(s.pas),
         mean.pas = mean(s.pas)) %>%
  ungroup()
```

## Plot

Some plots of within-team variability over time
```{r}
d %>%
  filter(team == 1001 | team == 1002 | team == 1003 | team == 1004 |
         team == 1005 | team == 1006 | team == 1007 | team == 1008) %>%
  ggplot(aes(x = m, y=sd.pas, color= team)) +
  geom_line(aes(y=sd.pas)) +
  labs(title = "Team-level passion variability across measurements", y = "Passion SD") +
   theme(legend.position="none") + 
  facet_wrap(~team)

```

> There does not seem to be much of a pattern in passion variability over time

## Using the standard deviation

Predicting within-team passion variance over time with "m" as predictor.
```{r}
# Random intercept
model_1 <- lme(fixed = sd.pas ~ m,
                   random = ~1 | team, 
                   data = d, 
                   na.action = na.omit)

summary(model_1)

# Random slope
model_1b <- lme(fixed = sd.pas ~ m,
                   random = ~m | team, 
                   data = d, 
                   na.action = na.omit)

summary(model_1b)

# Compare likelihoods (using ML instead of REML, otherwise likelihoods are not comparable)
model_1_r <- lme(fixed = sd.pas ~ m,
                   random = ~1 | team, 
                   data = d, 
                   na.action = na.omit, method = "ML")

model_1b_r <- lme(fixed = sd.pas ~ m,
                   random = ~m | team, 
                   data = d, 
                   na.action = na.omit, method = "ML")

anova(model_1_r, model_1b_r)

# Include the mean of passion (because of sd - mean confounding)
model_1c <- lme(fixed = sd.pas ~ m + mean.pas,
                   random = ~m | team, 
                   data = d, 
                   na.action = na.omit)

summary(model_1c)

# Compare likelihoods
model_1c_r <- lme(fixed = sd.pas ~ m + mean.pas,
                   random = ~m | team, 
                   data = d, 
                   na.action = na.omit, method = "ML", control = lmeControl(opt = "optim"))

anova(model_1b_r, model_1c_r)
```

> The third model (including mean passion score and random slope for m) has a better fit. In this model, there's no significant association between time and within-team passion variability.  

## Using the relative standard deviation

Relative variability index >>> this is a measure of variability that is not confounded by the mean. See also Mestdagh et al. (2018, http://dx.doi.org/10.1037/met0000153). 
```{r}
# Calculate relative variability rl.sd
rel.sd <- function(x) {
  relativeSD(x, MIN = 1, MAX=7)
}

d2 <- d %>%
  group_by(team, m) %>%
  mutate(rl.sd = rel.sd(s.pas))

# calculate relation bewteen mean and variability measures
rlin1=cor(d2$mean.pas, d2$sd.pas)
rlin2=cor(d2$mean.pas, d2$rl.sd, use = "complete.obs")
print(rlin1)
print(rlin2)

```

Predicting within-team passion variance over time using the relative sd.
```{r}
# Random intercept
model_2 <- lme(fixed = rl.sd ~ m,
                   random = ~1 | team, 
                   data = d2, 
                   na.action = na.omit)

summary(model_2)

# Random slope
model_2b <- lme(fixed = rl.sd ~ m,
                   random = ~m | team, 
                   data = d2, 
                   na.action = na.omit)

summary(model_2b)

# Check likelihoods
model_2_r <- lme(fixed = rl.sd ~ m,
                   random = ~1 | team, 
                   data = d2, 
                   na.action = na.omit, method = "ML")

model_2b_r <- lme(fixed = rl.sd ~ m,
                   random = ~m | team, 
                   data = d2, 
                   na.action = na.omit, method = "ML")

anova(model_2_r, model_2b_r)
```
> The second model (random slope) has a better fit. In this model there is no significant association between time and passion variability. 

## Modeling residual variances

```{r}
# Examine change in groups' latent means over time
step1 <- lme(s.pas ~ m, random =
             list(team = pdDiag(~1), pid = pdSymm(~1)),
             data = d, method = "ML", control = lmeControl(opt = "optim"))

# Examine variability in slopes
step2a <-update(step1, random = list(team = pdDiag(~m), pid=pdSymm(~1)))
summary(step2a)
VarCorr(step2a)

step2b <-update(step2a, random = list(team = pdSymm(~m), pid=pdSymm(~1)), 
                control = lmeControl(opt = "optim"))

summary(step2b)
VarCorr(step2b)

anova(step1, step2a, step2b)

# Examine whether there's a change in residual variance (i.e., consensus emergence) over time
step3 <- update(step2b, weights = varExp(form = ~ m))

anova(step1, step2a, step2b, step3)

summary(step3)$tTable
VarCorr(step3)

summary(step3)$modelStruct$varStruct
```

> Suggests residual variance increases over time (but only minimally), and therefore that team members become less similar in their passion scores.
